Staged Abstract Interpreters

### 2019-09-14 paper/20_prelim.tex
space

\begin{figure}[h!]
  \centering
  \vspace{-1em}
  \begin{subfigure}[b]{0.55\textwidth}
    \begin{lstlisting}
  trait Monad[M[_]] {
    def pure[A](a: A): M[A]
    def flatMap[A,B](ma: M[A])(f: A => M[B]): M[B]
  }
    \end{lstlisting}
    \vspace{-0.5em}
    \caption{trait \texttt{Monad}} \label{fig:monad}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.4\textwidth}
    \begin{lstlisting}
trait MonadOps[M[_], A] {
  def map[B](f: A => B): M[B]
  def flatMap[B](f: A => M[B]): M[B]
}
    \end{lstlisting}
    \vspace{-0.5em}
    \caption{trait \texttt{MonadOps}} \label{fig:monadops}
  \end{subfigure}
\end{figure}
\vspace{-1em}

@@

We also declare several operations to manipulate environments and
stores. These methods return monadic values of type @AnsM[_]@, which
may be parameterized over the environment or store type, or merely a @Unit@
value for performing effects. For example, @local_env@ installs a new environment
@ρ@ when evaluating the monadic value @ans@; @set_store@ takes a pair of
addresses and (potentially staged) values, and updates the store accordingly.

%\vspace{-1em}
\begin{figure}[h!]
  \centering
\vspace{-1em}
  \begin{subfigure}[b]{0.45\textwidth}
    \begin{lstlisting}
  type MonadOps[R[_], M[_], A] = {
    def map[B](f: R[A] => R[B]): M[B]
    def flatMap[B](f: R[A] => M[B]): M[B]
  }

  type AnsM[T] <: MonadOps[R, AnsM, T]
  type Ans = AnsM[Value]
    \end{lstlisting}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.55\textwidth}
    \begin{lstlisting}
// Environment operations
def ask_env: AnsM[Env]
def local_env(ans: Ans)(ρ: R[Env]): Ans
// Store operations
def get_store: AnsM[Store]
def put_store(σ: R[Store]): AnsM[Unit]
def set_store(av: (R[Addr], R[Value])): AnsM[Unit]
    \end{lstlisting}
  \end{subfigure}
\end{figure}
\vspace{-1em}

>>>>

\begin{figure}[h!]
  \centering
  \vspace{-1em}
  \begin{subfigure}[b]{0.55\textwidth}
    \begin{lstlisting}
  trait Monad[M[_]] {
    def pure[A](a: A): M[A]
    def flatMap[A,B](ma: M[A])(f: A => M[B]): M[B]
  }
    \end{lstlisting}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.4\textwidth}
    \begin{lstlisting}
trait MonadOps[M[_], A] {
  def map[B](f: A => B): M[B]
  def flatMap[B](f: A => M[B]): M[B]
}
    \end{lstlisting}
  \end{subfigure}
  \vspace{-1em}
  \caption{trait \texttt{Monad} (left) and trait \texttt{MonadOps} (right)} \label{fig:monad} \label{fig:monadops}
\end{figure}
\vspace{-1em}

@@

We also declare several operations to manipulate environments and
stores. These methods return monadic values of type @AnsM[_]@, which
may be parameterized over the environment or store type, or merely a @Unit@
value for performing effects. For example, @local_env@ installs a new environment
@ρ@ when evaluating the monadic value @ans@; @set_store@ takes a pair of
addresses and (potentially staged) values, and updates the store accordingly.
\begin{lstlisting}
  type MonadOps[R[_], M[_], A] = {           // Environment operations
    def map[B](f: R[A] => R[B]): M[B]        def ask_env: AnsM[Env]
    def flatMap[B](f: R[A] => M[B]): M[B]    def local_env(ans: Ans)(ρ: R[Env]): Ans
  }                                          // Store operations
                                             def get_store: AnsM[Store]
  type AnsM[T] <: MonadOps[R, AnsM, T]       def put_store(σ: R[Store]): AnsM[Unit]
  type Ans = AnsM[Value]                     def set_store(av: (R[Addr], R[Value])): AnsM[Unit]
\end{lstlisting}
